---
title: "260622_nmy-2_RNAi"
author: "Sam Zavislan-Pullaro"
date: "2026-06-22"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

## load libraries

```{r setup, echo = TRUE, warning = FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
library(data.table)
library(rstatix)

```


## Import the data that was outputted from the new macro:

Note: 

channel 1 = set-3

channel 2 = erm-1

```{r macroimport, echo = TRUE, warning = FALSE, message = FALSE}

# import the control data
# control data comes from L4440 empty vector RNAi controls 
control_1 <- read.table(file = "../01_input/2026-6-22_1458_datafile_for_230713_L4440_RNAi_rep1.txt", header = FALSE, sep = "\t")
control_2 <- read.table(file = "../01_input/2026-6-22_153_datafile_for_230828_L4440_RNAi_rep2.txt", header = FALSE, sep = "\t")
control_3 <- read.table(file = "../01_input/2026-6-22_156_datafile_for_240122_LP306_L4440-rep3.txt", header = FALSE, sep = "\t")


# import RNAi treatment data 
test_1 <- read.table(file = "../01_input/2026-6-24_1156_datafile_for_240113_NMY-2_RNAi-rep1.txt", header = FALSE, sep = "\t")
test_2 <- read.table(file = "../01_input/2026-6-24_122_datafile_for_240122_LP306_NMY-2.txt", header = FALSE, sep = "\t")
test_3 <- read.table(file = "../01_input/2026-6-24_129_datafile_for_240123_NMY-2_RNAi-rep2.txt", header = FALSE, sep = "\t")
test_4 <- read.table(file = "../01_input/2026-6-24_147_datafile_for_240221_LP306_NMY-2_RNAi-rep3.txt", header = FALSE, sep = "\t")

# test its dimensions
#dim(control_1)
#dim(control_2)
#dim(test_1)
#dim(test_2)
#dim(test_3)
#dim(test_4)

# Rename the column names
col_times <- paste(rep(1:333), sep = "")
colnames(control_1) <- c("file", "channel", col_times)
colnames(control_2) <- c("file", "channel", col_times)
colnames(control_3) <- c("file", "channel", col_times)

colnames(test_1) <- c("file", "channel", col_times)
colnames(test_2) <- c("file", "channel", col_times)
colnames(test_3) <- c("file", "channel", col_times)
colnames(test_4) <- c("file", "channel", col_times)

# Check that the dimensions remain unchanged
dim(control_1)
dim(control_2)
dim(control_3)

dim(test_1)
dim(test_2)
dim(test_3)
dim(test_4)



# control_1[1:9,1:8]
# control_2[1:9,1:8]
# control_3[1:9,1:8]

# test_1[1:9,1:8]
# test_2[1:9,1:8]
# test_3[1:9,1:8]
# test_4[1:9,1:8]

```


## Create annotation columns

```{r annotationcolumns, echo = TRUE, warning = FALSE, message = FALSE}

# Extract out the salient information from the filename and pivot the data longer - "permed" version
# Had to manually change image names to follow convention/consistency

control_1_exp <- control_1[2:dim(control_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_2_exp <- control_2[2:dim(control_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_3_exp <- control_3[2:dim(control_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

 
test_1_exp <- test_1[2:dim(test_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_2_exp <- test_2[2:dim(test_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_3_exp <- test_3[2:dim(test_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_4_exp <- test_4[2:dim(test_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))


```

```{r}
# Add in the timepoints

addInTimepoints <- function(tibble) {
  timepoints <- as.vector(unlist(control_1[1,3:335]))
  repnumb = dim(tibble)[1]/333
  tibble::add_column(tibble, timepoints = rep(timepoints,repnumb), .after = "xpoint")
}

control_1_plustime <- addInTimepoints(control_1_exp)
control_2_plustime <- addInTimepoints(control_2_exp)
control_3_plustime <- addInTimepoints(control_3_exp)

test_1_plustime <- addInTimepoints(test_1_exp)
test_2_plustime <- addInTimepoints(test_2_exp)
test_3_plustime <- addInTimepoints(test_3_exp)
test_4_plustime <- addInTimepoints(test_4_exp)

#check it
control_1_plustime[330:340,]
control_2_plustime[330:340,]
test_1_plustime[330:340,]
test_2_plustime[330:340,]
test_3_plustime[330:340,]
test_4_plustime[330:340,]
```

```{r}

# Merge the datasets together 
nmy2_RNAi_data_total <- rbind(control_1_plustime, control_2_plustime, control_3_plustime, test_1_plustime, test_2_plustime, test_3_plustime, test_4_plustime)

# Set explicit order for facets
nmy2_RNAi_data_total$treatment <- factor(nmy2_RNAi_data_total$treatment,
                                          levels = c("nmy-2", "L4440"))

# Plot it - all samples
ggplot(data = nmy2_RNAi_data_total, aes(x = timepoints, y = intensity, group = c(unique_id))) +
  geom_line(aes(colour = unique_id))+
  facet_wrap(~ channel + treatment)+
  guides(color = "none")+
  theme_bw()

```


## Align the erm-1 channel info

This step isn't really necessary but can help align the erm-1 samples based on the peak. Any associated set-3 samples come along for the ride.

Ideas - consider removing this step.

```{r splitmerge, echo = TRUE, warning = TRUE, message = TRUE}

# Split out channel 2
# channel_2_only <- nmy2_RNAi_data_total %>%
#   filter(channel == "ch2" & treatment == "L4440")
# unique(channel_2_only$embryoID, channel_2_only$date)
# # Split out channel 1
# channel_1_only <- nmy2_RNAi_data_total %>%
#   filter(channel == "ch1" | treatment == "nmy-2")

channel_2_only <- nmy2_RNAi_data_total %>%
  filter(channel == "ch2")

channel_1_only <- nmy2_RNAi_data_total %>%
  filter(channel == "ch1")

# Check that everything worked
dim(nmy2_RNAi_data_total)
dim(channel_2_only)
dim(channel_1_only)

# Align by finding max per variable and adjusting row_id
channel_2_dt <- as.data.table(channel_2_only)
#channel_2_only
channel_2_dt$xpoint <- as.integer(channel_2_dt$xpoint)
channel_2_dt[, aligned_row := xpoint - (which.max(intensity) - 1), by = unique_id]
#channel_2_dt
channel2_dcast <- dcast(channel_2_dt, strain + aligned_row ~ unique_id, value.var = "intensity")

#channel2_dcast
dim(channel2_dcast)

# Create align rows for channel 1
channel_1_dt <- as.data.table(channel_1_only)
channel_1_dt$xpoint <- as.integer(channel_1_dt$xpoint)

# Create an aligned row for channel 1
dim(channel_1_dt)[1]
head(channel_1_dt)
iterations = dim(channel_1_dt)[1]/333
aligned_row = rep(-166:166, iterations)
length(aligned_row)
channel_1_dt <- cbind(channel_1_dt, aligned_row)
channel1_dcast <- dcast(channel_1_dt, strain + aligned_row ~ unique_id, value.var = "intensity")

dim(channel1_dcast)

# Merge back together
# Pivot long - ch2 Modified this!!!
colnames(channel2_dcast)
ch2_align_long <- channel2_dcast %>%
  pivot_longer(cols = -c(strain, aligned_row), names_to = "unique_id", values_to = "intensity")
#channel2_dcast

# pivot long - ch1 Modified this!!!
colnames(channel1_dcast)
ch1_align_long <- channel1_dcast %>%
  pivot_longer(cols = -c(strain, aligned_row), names_to = "unique_id", values_to = "intensity")

# Check that all the colnames and data types match
colnames(ch2_align_long)
colnames(ch1_align_long)
str(ch2_align_long)
str(ch1_align_long)
ch1_align_long$aligned_row <- as.numeric(ch1_align_long$aligned_row )

# Merge back together
total_align_long <- rbind(ch2_align_long, ch1_align_long)

```

```{r}
total_align_long %>%
  group_by(aligned_row) %>%
  summarize(
    n_total = n(),
    n_na = sum(is.na(intensity)),
    pct_na = mean(is.na(intensity)) * 100
  ) %>%
  arrange(aligned_row) %>%
  print(n = Inf)
```


## re-arrange the dataset and calculate the means 

```{r meanplot, echo = TRUE, warning = FALSE, message = FALSE}



# Normalize the data by dividing by the embryo-specific mean
# nmy2_norm_total <- total_align_long %>%
#   separate_wider_delim(unique_id, delim = "_", names = c("date", NA, "treatment", "embryoID", "channel")) %>%
#   group_by(date, embryoID, channel, treatment) %>%
#   mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE))
# table(nmy2_norm_total$channel, nmy2_norm_total$treatment)

# Normalize the data by dividing by the embryo-specific mean
nmy2_norm_total <- total_align_long %>%
  separate_wider_delim(unique_id, delim = "_", names = c("date", NA, "treatment", "embryoID", "channel")) %>%
  mutate(treatment = factor(treatment, levels = c("nmy-2", "L4440"))) %>%
  group_by(date, embryoID, channel, treatment) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE))

head(nmy2_norm_total)

# Separate out the unique identifier info, then pivot sider
nmy2_wide_by_sample <- nmy2_norm_total %>%
  pivot_wider(names_from = c(date, embryoID, channel, treatment), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row))


# Second Try - Separate out the unique identifier info, then pivot sider
nmy2_wide_by_sample <- nmy2_norm_total %>%
  pivot_wider(names_from = c(date, embryoID), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row, treatment, channel))



colnames(nmy2_wide_by_sample)
# Play around with mean, medium, and sum:

nmy2_wide_with_stats <- nmy2_wide_by_sample %>%
  rowwise() %>%
  mutate(
    sum_signal    = sum(c_across(`230713_03`:`240123_13`), na.rm = TRUE),
    mean_signal   = mean(c_across(`230713_03`:`240123_13`), na.rm = TRUE),
    median_signal = median(c_across(`230713_03`:`240123_13`), na.rm = TRUE),
    sd_signal     = sd(c_across(`230713_03`:`240123_13`), na.rm = TRUE)
  ) %>%
  ungroup()

colnames(nmy2_wide_with_stats)

nmy2_wide_with_range <- nmy2_wide_with_stats %>%
  rowwise() %>%
  mutate(ymeanmax = sum(mean_signal, sd_signal) ) %>%
  mutate(ymeanmin = sum(mean_signal, -sd_signal)) 

colorselection = c("#000000", "#2189ce")

# Plot split by RNAi treatment
a <- ggplot(data = nmy2_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=channel))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("set-1 mRNA", "erm-1 mRNA"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=channel), alpha = 0.2, ) +
  facet_wrap(~ treatment)+
  theme_bw()

a


#pdf(file = "../03_outputPlots/.pdf", width = 4, height = 3)

a

dev.off()


# Plot in a different way - set-3 and erm-1 mRNA split into facets
colorselection = c("#2189ce", "#000000")
channel.labs <- c("set-3 mRNA", "erm-1 mRNA")
names(channel.labs) <- c("ch1", "ch2")

# Plot split by transcript
b <- ggplot(data = nmy2_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=treatment))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("control", "nmy-2 RNAi"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=treatment), alpha = 0.2, ) +
  facet_wrap(~ channel, labeller = labeller(channel = channel.labs))+
  theme_bw()

b


# pdf(file = "../03_outputPlots/.pdf", width = 4, height = 3)
# 
# b

dev.off()

```


## Try to create a metric of "membrane-y-ness" for each condition combo

I want a metric that reports the ratio of erm-1 intensity signal at "0" (the peak) versus at -100 or +100. I'll
take the average of -100 and +100.

```{r membraneyness, echo = TRUE, warning = FALSE, message = FALSE}

# extract the "peak" at 1 versus the -100 and +100 values
peaks_and_valleys <- nmy2_norm_total %>%
  filter(aligned_row %in% c(-100,1,100)) 

# Nest the -100, 1, and +100 values into a single cell
nest_pandv <- peaks_and_valleys %>%
  group_by(date, treatment, embryoID, channel) %>%
  nest()

# A function to calculate the ratio of the value at 1 compared to the mean of -100 and +100
# my_calc2 <- function(df) {
#   df$normalized_intensity[2] / mean(df$normalized_intensity[1], df$normalized_intensity[3])
# }

my_calc2 <- function(df) {
  df$normalized_intensity[2] / mean(c(df$normalized_intensity[1], df$normalized_intensity[3]))
}

# Calculate the ratio for each datapoint
foldChange_calc <- nest_pandv %>%
  mutate(fc_enrich = map_dbl(data, my_calc2))

# Change some columns to factors
foldChange_calc$treatment <- as.factor(foldChange_calc$treatment)
foldChange_calc$channel <- as.factor(foldChange_calc$channel)

# calculate the max & min - figure out how to set the y-axis
summary(log(foldChange_calc$fc_enrich, base = 2))

# plot the data:
d <- ggplot(data = foldChange_calc, aes(x = as.factor(channel), y = log(fc_enrich, base = 2), fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("L4440" = "darkgray", "nmy-2" = "lightblue"),
                   labels = c("L4440" = "L4440 control", "nmy-2" = "nmy-2 RNAi"))+labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -100 and 100)", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 12)

d

e <- ggplot(data = foldChange_calc, aes(x = as.factor(treatment), y = log(fc_enrich, base = 2), fill = channel))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -100 and 100)", x = "mRNA") +
  theme_classic(base_size = 12)

e

getwd()

```
```{r}
library(dplyr)

foldChange_calc %>%
  group_by(treatment, channel) %>%
  summarise(
    min_val    = min(log(fc_enrich, base = 2), na.rm = TRUE),
    median_val = median(log(fc_enrich, base = 2), na.rm = TRUE),
    max_val    = max(log(fc_enrich, base = 2), na.rm = TRUE)
  )
```
```{r}
foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  slice(c(
    which.min(log2_fc),
    which(log2_fc == median(log2_fc)), 
    which.max(log2_fc)
  ))
```
```{r}
df <- foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  mutate(med = median(log2_fc))

label_points <- bind_rows(
  df %>% slice(which.min(log2_fc))              %>% mutate(label = "min"),
  df %>% slice(which.min(abs(log2_fc - med)))   %>% mutate(label = "median"),
  df %>% slice(which.max(log2_fc))              %>% mutate(label = "max")
)
```

```{r}
foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  filter(log2_fc == min(log2_fc) | log2_fc == max(log2_fc))
```
```{r}
library(ggrepel)

df <- foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  mutate(med = median(log2_fc))

label_points <- bind_rows(
  df %>% slice(which.min(log2_fc))            %>% mutate(label = "min"),
  df %>% slice(which.min(abs(log2_fc - med))) %>% mutate(label = "median"),
  df %>% slice(which.max(log2_fc))            %>% mutate(label = "max")
) %>%
  # Keep only one label per row — if min/median/max land on same row, 
  # priority: min > max > median
  group_by(treatment, channel, date, embryoID) %>%
  slice(1) %>%
  ungroup()

```

```{r}
label_points <- bind_rows(
  df %>% slice(which.min(log2_fc)) %>% mutate(label = "min"),
  df %>% slice(which.max(log2_fc)) %>% mutate(label = "max"),
  df %>% filter(n() >= 3) %>% 
         slice(which.min(abs(log2_fc - med))) %>% mutate(label = "median")
) %>%
  distinct(treatment, channel, date, embryoID, .keep_all = TRUE)
```

```{r}
library(ggrepel)

e + geom_label_repel(
  data = label_points,
  aes(x = as.factor(treatment), y = log2_fc,
      label = paste(label, paste(date, embryoID, sep = "_"), sep = ": "),
      fill = channel),
  position = position_dodge(width = 0.75),  # matches geom_boxplot default
  size = 3,
  alpha = 0.8,
  max.overlaps = 20,
  show.legend = FALSE
)
```
## Save the datasets

```{print_data, echo = TRUE, warning = FALSE, message = FALSE}

# set plotname
today <- format(Sys.Date(), "%y%m%d")
filename <- paste("../03_outputPlots/", today, "nmy-2_L4440.pdf", sep = "")

pdf(filename, width = 6, height = 6)
d
dev.off()

getwd()


```

## Calculate the statistics

```{r wilcox, echo = TRUE, warning = FALSE, message = FALSE}

foldChange_calc

stats_wilcox <- foldChange_calc %>%
  group_by(channel) %>%
  wilcox_test(fc_enrich ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox


```
```{r}
### Run Welch's t-test to confirm same result 
stats_ttest <- foldChange_calc %>%
  group_by(channel) %>%
  t_test(fc_enrich ~ treatment) %>%
  group_by(channel) %>%              # re-add grouping, lost by t_test()
  adjust_pvalue(method = "BH") %>%
  add_significance()
stats_ttest
```



## Session info

```{r sessionInfo, echo = TRUE, warning = FALSE, message = FALSE}

sessionInfo()

```