---
title: "260622_klp-19_RNAi"
author: "Sam Zavislan-Pullaro"
date: "2026-07-14"
output:
  html_document:
    toc: true
    toc_depth: 4
---

## load libraries

```{r setup, echo = TRUE, warning = FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
library(data.table)
library(rstatix)

```


## Import the data that was outputted from the new macro:

Note:

channel 1 = set-3

channel 2 = erm-1

```{r macroimport, echo = TRUE, warning = FALSE, message = FALSE}

# import the control data
# control data comes from L4440 empty vector RNAi controls
control_1 <- read.table(file = "../01_input/2026-6-22_1458_datafile_for_230713_L4440_RNAi_rep1.txt", header = FALSE, sep = "\t")
control_2 <- read.table(file = "../01_input/2026-6-22_153_datafile_for_230828_L4440_RNAi_rep2.txt", header = FALSE, sep = "\t")
control_3 <- read.table(file = "../01_input/2026-6-22_156_datafile_for_240122_LP306_L4440-rep3.txt", header = FALSE, sep = "\t")


# import RNAi treatment data
test_1 <- read.table(file = "../01_input/2026-6-22_1335_datafile_for_231228_LP306_KLP-19-rep1.txt", header = FALSE, sep = "\t")
test_2 <- read.table(file = "../01_input/2026-6-23_174_datafile_for_240122_LP306_KLP-19-rep2.txt", header = FALSE, sep = "\t")
test_3 <- read.table(file = "../01_input/2026-6-23_1712_datafile_for_240123_LP306_KLP-19_rep3.txt", header = FALSE, sep = "\t")

# Rename the column names
col_times <- paste(rep(1:333), sep = "")
colnames(control_1) <- c("file", "channel", col_times)
colnames(control_2) <- c("file", "channel", col_times)
colnames(control_3) <- c("file", "channel", col_times)

colnames(test_1) <- c("file", "channel", col_times)
colnames(test_2) <- c("file", "channel", col_times)
colnames(test_3) <- c("file", "channel", col_times)

# Check that the dimensions remain unchanged
dim(control_1)
dim(control_2)
dim(control_3)

dim(test_1)
dim(test_2)
dim(test_3)

```


## Create annotation columns

```{r annotationcolumns, echo = TRUE, warning = FALSE, message = FALSE}

# Extract out the salient information from the filename and pivot the data longer - "permed" version
# Had to manually change image names to follow convention/consistency

control_1_exp <- control_1[2:dim(control_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

control_2_exp <- control_2[2:dim(control_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

control_3_exp <- control_3[2:dim(control_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))


test_1_exp <- test_1[2:dim(test_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_2_exp <- test_2[2:dim(test_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_3_exp <- test_3[2:dim(test_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

```

```{r}
# Add in the timepoints

addInTimepoints <- function(tibble) {
  timepoints <- as.vector(unlist(control_1[1,3:335]))
  repnumb = dim(tibble)[1]/333
  tibble::add_column(tibble, timepoints = rep(timepoints,repnumb), .after = "xpoint")
}

control_1_plustime <- addInTimepoints(control_1_exp)
control_2_plustime <- addInTimepoints(control_2_exp)
control_3_plustime <- addInTimepoints(control_3_exp)

test_1_plustime <- addInTimepoints(test_1_exp)
test_2_plustime <- addInTimepoints(test_2_exp)
test_3_plustime <- addInTimepoints(test_3_exp)

#check it
control_1_plustime[330:340,]
control_2_plustime[330:340,]
test_1_plustime[330:340,]
test_2_plustime[330:340,]
test_3_plustime[330:340,]
```

```{r}

# Merge the datasets together
rnai_data_total <- rbind(control_1_plustime, control_2_plustime, control_3_plustime, test_1_plustime, test_2_plustime, test_3_plustime)

# Plot it - all samples
ggplot(data = rnai_data_total, aes(x = timepoints, y = intensity, group = c(unique_id))) +
  geom_line(aes(colour = unique_id))+
  facet_wrap(~ channel + treatment)+
  guides(color = "none")+
  theme_bw()

```


## Skip peak alignment - use fixed coordinate instead

Alignment step removed (prior discussion: aligning each embryo to its own
observed channel-2 peak risks manufacturing apparent enrichment at the
alignment point, since by construction that point is the brightest value in
every embryo). Instead, every embryo uses the same fixed coordinate system
based on its row position (`xpoint`), recentered so it spans the same
`-166:166` range the old aligned coordinate used. This keeps every downstream
chunk (normalization, wide pivot, stats, plots, membraneyness calc) working
on a column still called `aligned_row`, with no other code changes required.

```{r splitmerge, echo = TRUE, warning = TRUE, message = TRUE}

# No channel split needed here anymore - alignment was the only reason
# channel 1 and channel 2 were ever separated at this stage. Both channels
# get the same fixed coordinate, so we recenter the whole dataset at once.

rnai_dt <- as.data.table(rnai_data_total)
rnai_dt$xpoint <- as.integer(rnai_dt$xpoint)

# Fixed coordinate: recenter xpoint (1:333) to run -166:166, identical for
# every embryo and every channel - no peak-finding, no per-embryo offset.
rnai_dt[, aligned_row := xpoint - 167]

# Check that everything worked
dim(rnai_data_total)
dim(rnai_dt)
range(rnai_dt$aligned_row)

# Rename to match the variable name the rest of the script expects
total_align_long <- rnai_dt %>%
  select(strain, aligned_row, unique_id, intensity)

```

```{r}
total_align_long %>%
  group_by(aligned_row) %>%
  summarize(
    n_total = n(),
    n_na = sum(is.na(intensity)),
    pct_na = mean(is.na(intensity)) * 100
  ) %>%
  arrange(aligned_row) %>%
  print(n = Inf)
```

## Generate .csv of max intensities for erm-1 in klp-19 KD and L4440 control

```{r}
max_intensities <- total_align_long %>%
  filter(!grepl("ch1", unique_id)) %>% # filter out rows that contain set-3 in ch1
  group_by(unique_id) %>%
  slice_max(intensity, n = 1, with_ties = FALSE)

write_csv(max_intensities, "klp-19_L4440_ch2_max_intensities.csv")
```


## re-arrange the dataset and calculate the means

```{r meanplot, echo = TRUE, warning = FALSE, message = FALSE}

# Normalize the data by dividing by the embryo-specific mean
rnai_norm_total <- total_align_long %>%
  separate_wider_delim(unique_id, delim = "_", names = c("date", NA, "treatment", "embryoID", "channel")) %>%
  group_by(date, embryoID, channel, treatment) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE))
table(rnai_norm_total$channel, rnai_norm_total$treatment)

head(rnai_norm_total)

```

## Visualize how normalization is affecting y-axis

```{r}
ggplot(data = rnai_norm_total, aes(x = aligned_row, y = normalized_intensity,
                                     group = interaction(date, embryoID, channel))) +
  geom_line(aes(color = interaction(date, embryoID, channel)), alpha = 0.5) +
  facet_wrap(~ channel + treatment) +
  guides(color = "none") +
  theme_bw()
```

```{r}
# Separate out the unique identifier info, then pivot wider
rnai_wide_by_sample <- rnai_norm_total %>%
  pivot_wider(names_from = c(date, embryoID),
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row, treatment, channel))

colnames(rnai_wide_by_sample)

rnai_wide_with_stats <- rnai_wide_by_sample %>%
  rowwise() %>%
  mutate(
    sum_signal    = sum(c_across(`230713_03`:`240123_10`), na.rm = TRUE),
    mean_signal   = mean(c_across(`230713_03`:`240123_10`), na.rm = TRUE),
    median_signal = median(c_across(`230713_03`:`240123_10`), na.rm = TRUE),
    sd_signal     = sd(c_across(`230713_03`:`240123_10`), na.rm = TRUE)
  ) %>%
  ungroup()

rnai_wide_with_range <- rnai_wide_with_stats %>%
  rowwise() %>%
  mutate(ymeanmax = sum(mean_signal, sd_signal) ) %>%
  mutate(ymeanmin = sum(mean_signal, -sd_signal))

colorselection = c("#000000", "#2189ce")

# Plot split by RNAi treatment and L4440 empty vector control
a <- ggplot(data = rnai_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=channel))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("set-1 mRNA", "erm-1 mRNA"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=channel), alpha = 0.2, ) +
  facet_wrap(~ treatment)+
  theme_bw()

a


# Plot in a different way - set-3 and erm-1 mRNA split into facets
colorselection = c("#2189ce", "#000000")
channel.labs <- c("set-3 mRNA", "erm-1 mRNA")
names(channel.labs) <- c("ch1", "ch2")

# Plot split by transcript
b <- ggplot(data = rnai_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=treatment))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("control", "klp-19 RNAi"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=treatment), alpha = 0.2, ) +
  facet_wrap(~ channel, labeller = labeller(channel = channel.labs))+
  theme_bw()

```


## Try to create a metric of "membrane-y-ness" for each condition combo

I want a metric that reports the ratio of erm-1 intensity signal at "0" (the peak) versus at -100 or +100. I'll
take the average of -100 and +100.

```{r membraneyness, echo = TRUE, warning = FALSE, message = FALSE}

# extract the "peak" at 1 versus the -100 and +100 values
peaks_and_valleys <- rnai_norm_total %>%
  filter(aligned_row %in% c(-100,1,100))

# Nest the -100, 1, and +100 values into a single cell
nest_pandv <- peaks_and_valleys %>%
  group_by(date, treatment, embryoID, channel) %>%
  nest()

# A function to calculate the ratio of the value at 1 compared to the mean of -100 and +100
my_calc2 <- function(df) {
  df$normalized_intensity[2] / mean(c(df$normalized_intensity[1], df$normalized_intensity[3]))
}

# Calculate the ratio for each datapoint
foldChange_calc <- nest_pandv %>%
  mutate(fc_enrich = map_dbl(data, my_calc2))

# Change some columns to factors
foldChange_calc$treatment <- as.factor(foldChange_calc$treatment)
foldChange_calc$channel <- as.factor(foldChange_calc$channel)

# calculate the max & min - figure out how to set the y-axis
summary(log(foldChange_calc$fc_enrich, base = 2))

# plot the data:
d <- ggplot(data = foldChange_calc, aes(x = as.factor(channel), y = log(fc_enrich, base = 2), fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("L4440" = "darkgray", "klp-19" = "lightblue"),
                   labels = c("L4440" = "L4440 control", "klp-19" = "klp-19 RNAi"))+
  labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -100 and 100)", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 12)

d

e <- ggplot(data = foldChange_calc, aes(x = as.factor(treatment), y = log(fc_enrich, base = 2), fill = channel))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -100 and 100)", x = "mRNA") +
  theme_classic(base_size = 12)

e

getwd()

```
```{r}
library(dplyr)

foldChange_calc %>%
  group_by(treatment, channel) %>%
  summarise(
    min_val    = min(log(fc_enrich, base = 2), na.rm = TRUE),
    median_val = median(log(fc_enrich, base = 2), na.rm = TRUE),
    max_val    = max(log(fc_enrich, base = 2), na.rm = TRUE)
  )
```
```{r}
foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  slice(c(
    which.min(log2_fc),
    which(log2_fc == median(log2_fc)),
    which.max(log2_fc)
  ))
```
```{r}
df <- foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  mutate(med = median(log2_fc))

label_points <- bind_rows(
  df %>% slice(which.min(log2_fc))              %>% mutate(label = "min"),
  df %>% slice(which.min(abs(log2_fc - med)))   %>% mutate(label = "median"),
  df %>% slice(which.max(log2_fc))              %>% mutate(label = "max")
)
```

```{r}
foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  filter(log2_fc == min(log2_fc) | log2_fc == max(log2_fc))
```
```{r}
library(ggrepel)

df <- foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  mutate(med = median(log2_fc))

label_points <- bind_rows(
  df %>% slice(which.min(log2_fc))            %>% mutate(label = "min"),
  df %>% slice(which.min(abs(log2_fc - med))) %>% mutate(label = "median"),
  df %>% slice(which.max(log2_fc))            %>% mutate(label = "max")
) %>%
  # Keep only one label per row — if min/median/max land on same row,
  # priority: min > max > median
  group_by(treatment, channel, date, embryoID) %>%
  slice(1) %>%
  ungroup()

```

```{r}
label_points <- bind_rows(
  df %>% slice(which.min(log2_fc)) %>% mutate(label = "min"),
  df %>% slice(which.max(log2_fc)) %>% mutate(label = "max"),
  df %>% filter(n() >= 3) %>%
         slice(which.min(abs(log2_fc - med))) %>% mutate(label = "median")
) %>%
  distinct(treatment, channel, date, embryoID, .keep_all = TRUE)
```

```{r}
library(ggrepel)

e + geom_label_repel(
  data = label_points,
  aes(x = as.factor(treatment), y = log2_fc,
      label = paste(label, paste(date, embryoID, sep = "_"), sep = ": "),
      fill = channel),
  position = position_dodge(width = 0.75),  # matches geom_boxplot default
  size = 3,
  alpha = 0.8,
  max.overlaps = 20,
  show.legend = FALSE
)
```

## Save the datasets

```{print_data, echo = TRUE, warning = FALSE, message = FALSE}

# set plotname
today <- format(Sys.Date(), "%y%m%d")
filename <- paste("../03_outputPlots/", today, "klp-19_L4440.pdf", sep = "")

pdf(filename, width = 6, height = 6)
d
dev.off()

getwd()


```

## Calculate the statistics

```{r wilcox, echo = TRUE, warning = FALSE, message = FALSE}

foldChange_calc

stats_wilcox <- foldChange_calc %>%
  group_by(channel) %>%
  wilcox_test(fc_enrich ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox


```
```{r}
### Run Welch's t-test to confirm same result
stats_ttest <- foldChange_calc %>%
  group_by(channel) %>%
  t_test(fc_enrich ~ treatment) %>%
  group_by(channel) %>%              # re-add grouping, lost by t_test()
  adjust_pvalue(method = "BH") %>%
  add_significance()
stats_ttest
```



## Session info

```{r sessionInfo, echo = TRUE, warning = FALSE, message = FALSE}

sessionInfo()

```
