---
title: "260527_bmk1_RNAi"
author: "Sam Zavislan-Pullaro"
date: "2026-05-27"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

## load libraries

```{r setup, echo = TRUE, warning = FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
library(data.table)
library(rstatix)

```


## Import the data that was outputted from the new macro:

Note: 

channel 1 = set-3

channel 2 = erm-1

```{r macroimport, echo = TRUE, warning = FALSE, message = FALSE}

# import the control data
# control data comes from no RNAi set-3 erm-1 controls 
control_1 <- read.table(file = "../01_input/2026-5-21_162_datafile_for_221011_LP306_no_treatment.txt", header = FALSE, sep = "\t")
control_2 <- read.table(file = "../01_input/2026-5-21_1642_datafile_for_240610_LP306_erm-1.txt", header = FALSE, sep = "\t")
control_3 <- read.table(file = "../01_input/2026-5-26_1047_datafile_for_240621_LP306_erm-1_set-3.txt", header = FALSE, sep = "\t")
control_4 <- read.table(file = "../01_input/2026-5-26_1130_datafile_for_240701_LP306_erm-1_set-3.txt", header = FALSE, sep = "\t")

# import RNAi treatment data 
test_1 <- read.table(file = "../01_input/2026-5-26_1149_datafile_for_220719_LP306_bmk-1_RNAi.txt", header = FALSE, sep = "\t")
test_2 <- read.table(file = "../01_input/2026-5-29_1454_datafile_for_230408_LP306_BMK-1_rep1.txt", header = FALSE, sep = "\t")
test_3 <- read.table(file = "../01_input/2026-5-26_1242_datafile_for_231107_LP306_BMK-1_rep2.txt", header = FALSE, sep = "\t")
test_4 <- read.table(file = "../01_input/2026-5-26_1449_datafile_for_231113_LP306_BMK-1_rep3.txt", header = FALSE, sep = "\t")

# test its dimensions
#dim(control_1)
#dim(control_2)
#dim(test_1)
#dim(test_2)
#dim(test_3)
#dim(test_4)

# Rename the column names
col_times <- paste(rep(1:333), sep = "")
colnames(control_1) <- c("file", "channel", col_times)
colnames(control_2) <- c("file", "channel", col_times)
colnames(control_3) <- c("file", "channel", col_times)
colnames(control_4) <- c("file", "channel", col_times)
colnames(test_1) <- c("file", "channel", col_times)
colnames(test_2) <- c("file", "channel", col_times)
colnames(test_3) <- c("file", "channel", col_times)
colnames(test_4) <- c("file", "channel", col_times)

# Check that the dimensions remain unchanged
dim(control_1)
dim(control_2)
dim(control_3)
dim(control_4)
dim(test_1)
dim(test_2)
dim(test_3)
dim(test_4)


# control_1[1:9,1:8]
# control_2[1:9,1:8]
# control_3[1:9,1:8]
# control_4[1:9,1:8]
# test_1[1:9,1:8]
# test_2[1:9,1:8]
# test_3[1:9,1:8]
# test_4[1:9,1:8]

```


## Create annotation columns

```{r annotationcolumns, echo = TRUE, warning = FALSE, message = FALSE}

# Extract out the salient information from the filename and pivot the data longer - "permed" version
# Had to manually change image names to follow convention/consistency

control_1_exp <- control_1[2:dim(control_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_2_exp <- control_2[2:dim(control_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_3_exp <- control_3[2:dim(control_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

control_4_exp <- control_4[2:dim(control_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
test_1_exp <- test_1[2:dim(test_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_2_exp <- test_2[2:dim(test_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_3_exp <- test_3[2:dim(test_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_4_exp <- test_4[2:dim(test_4)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

```

```{r}
# Add in the timepoints

addInTimepoints <- function(tibble) {
  timepoints <- as.vector(unlist(control_1[1,3:335]))
  repnumb = dim(tibble)[1]/333
  tibble::add_column(tibble, timepoints = rep(timepoints,repnumb), .after = "xpoint")
}

control_1_plustime <- addInTimepoints(control_1_exp)
control_2_plustime <- addInTimepoints(control_2_exp)
control_3_plustime <- addInTimepoints(control_3_exp)
control_4_plustime <- addInTimepoints(control_4_exp)
test_1_plustime <- addInTimepoints(test_1_exp)
test_2_plustime <- addInTimepoints(test_2_exp)
test_3_plustime <- addInTimepoints(test_3_exp)
test_4_plustime <- addInTimepoints(test_4_exp)

# check it
# control_1_plustime[330:340,]
# control_2_plustime[330:340,]
# test_1_plustime[330:340,]
# test_2_plustime[330:340,]
# test_3_plustime[330:340,]
# test_4_plustime[330:340,]
```

```{r}

# Merge the datasets together 
bmk1_RNAi_data_total <- rbind(control_1_plustime, control_2_plustime, 
                              control_3_plustime, control_4_plustime, 
                              test_1_plustime, test_2_plustime, 
                              test_3_plustime, test_4_plustime) %>%
  mutate(xpoint = as.integer(xpoint))

# Plot it - all samples
ggplot(data = bmk1_RNAi_data_total, aes(x = timepoints, y = intensity, group = c(unique_id))) +
  geom_line(aes(colour = unique_id))+
  facet_wrap(~ channel + treatment)+
  guides(color = "none")+
  theme_bw()

```


## Align the erm-1 channel info

This step isn't really necessary but can help align the erm-1 samples based on the peak. Any associated set-3 samples come along for the ride.

Ideas - consider removing this step.

```{r splitmerge, echo=TRUE, message=TRUE, warning=TRUE}

# Split out channel 2
# channel_2_only <- bmk1_RNAi_data_total %>%
#   filter(channel == "ch2" & treatment == "control")
# unique(channel_2_only$embryoID, channel_2_only$date)
# # Split out channel 1
# channel_1_only <- bmk1_RNAi_data_total %>%
#   filter(channel == "ch1" | treatment == "bmk-1-RNAi")
# 
# # Check that everything worked
# dim(bmk1_RNAi_data_total)
# dim(channel_2_only)
# dim(channel_1_only)
# 
# # Align by finding max per variable and adjusting row_id
# channel_2_dt <- as.data.table(channel_2_only)
# #channel_2_only
# channel_2_dt$xpoint <- as.integer(channel_2_dt$xpoint)
# channel_2_dt[, aligned_row := xpoint - (which.max(intensity) - 1), by = unique_id]
# #channel_2_dt
# channel2_dcast <- dcast(channel_2_dt, strain + aligned_row ~ unique_id, value.var = "intensity")
# 
# #channel2_dcast
# dim(channel2_dcast)
# 
# # Create align rows for channel 1
# channel_1_dt <- as.data.table(channel_1_only)
# channel_1_dt$xpoint <- as.integer(channel_1_dt$xpoint)
# 
# # Create an aligned row for channel 1
# dim(channel_1_dt)[1]
# head(channel_1_dt)
# iterations = dim(channel_1_dt)[1]/333
# aligned_row = rep(-166:166, iterations)
# length(aligned_row)
# channel_1_dt <- cbind(channel_1_dt, aligned_row)
# channel1_dcast <- dcast(channel_1_dt, strain + aligned_row ~ unique_id, value.var = "intensity")
# 
# dim(channel1_dcast)
# 
# # Merge back together
# # Pivot long - ch2
# colnames(channel2_dcast)
# ch2_align_long <- channel2_dcast %>%
#   pivot_longer(cols = (`221011_LP306_control_06_ch2`:`240701_LP306_control_09_ch2`), names_to = "unique_id", values_to = "intensity")
# 
# #channel2_dcast
# 
# # pivot long - ch1
# colnames(channel1_dcast)
# ch1_align_long <- channel1_dcast %>%
#   pivot_longer(cols = (`220719_LP306_bmk-1-RNAi_01_ch1`:`240701_LP306_control_09_ch1`), names_to = "unique_id", values_to = "intensity")
# 
# # Check that all the colnames and data types match
# colnames(ch2_align_long)
# colnames(ch1_align_long)
# str(ch2_align_long)
# str(ch1_align_long)
# ch1_align_long$aligned_row <- as.numeric(ch1_align_long$aligned_row )
# 
# # Merge back together
# total_align_long <- rbind(ch2_align_long, ch1_align_long)

```

```{r}
# total_align_long %>%
#   group_by(aligned_row) %>%
#   summarize(
#     n_total = n(),
#     n_na = sum(is.na(intensity)),
#     pct_na = mean(is.na(intensity)) * 100
#   ) %>%
#   arrange(aligned_row) %>%
#   print(n = Inf)
```


## re-arrange the dataset and calculate the means 
```{r meanplot, echo = TRUE, warning = FALSE, message = FALSE}

# Normalize the data by dividing by the embryo-specific mean
# Each embryo's intensity profile gets divided by its own mean intensity,
# so values represent fold-change relative to that embryo's average signal.
bmk1_norm_total <- bmk1_RNAi_data_total %>%
  group_by(date, embryoID, channel, treatment) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE)) %>%
  ungroup()

# Sanity check: how many embryo measurements per channel × treatment?
table(bmk1_norm_total$channel, bmk1_norm_total$treatment)

# Pivot wider so each embryo becomes its own column.
# Rows are uniquely identified by xpoint × channel × treatment.
# Cells contain that embryo's normalized intensity at that xpoint
# (or NA if the embryo doesn't belong to that channel/treatment combination).
bmk1_wide_by_sample <- bmk1_norm_total %>%
  pivot_wider(names_from = c(date, embryoID), 
              values_from = normalized_intensity,
              id_cols = c(strain, xpoint, treatment, channel))

# Identify which columns hold per-embryo data (everything except the ID columns)
id_cols <- c("strain", "xpoint", "treatment", "channel")
embryo_cols <- setdiff(colnames(bmk1_wide_by_sample), id_cols)

# Compute per-row summary statistics across embryos.
# na.rm = TRUE because each row only has data for embryos matching its channel/treatment.
bmk1_wide_with_stats <- bmk1_wide_by_sample %>%
  rowwise() %>%
  mutate(
    n_contributing = sum(!is.na(c_across(all_of(embryo_cols)))),
    sum_signal     = sum(c_across(all_of(embryo_cols)), na.rm = TRUE),
    mean_signal    = mean(c_across(all_of(embryo_cols)), na.rm = TRUE),
    median_signal  = median(c_across(all_of(embryo_cols)), na.rm = TRUE),
    sd_signal      = sd(c_across(all_of(embryo_cols)), na.rm = TRUE),
    sem_signal     = sd_signal / sqrt(n_contributing)
  ) %>%
  ungroup() %>%
  mutate(
    # Ribbon bounds: mean ± SD (swap sd_signal for sem_signal if you want SEM instead)
    ymeanmax = mean_signal + sd_signal,
    ymeanmin = mean_signal - sd_signal
  )

# ----- Plot 1: split by treatment, color by channel -----
colorselection_channel <- c("#000000", "#2189ce")

a <- ggplot(bmk1_wide_with_stats, 
            aes(x = xpoint, y = mean_signal, 
                group = interaction(channel, treatment))) +
  geom_line(aes(color = channel)) +
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill = channel), alpha = 0.2) +
  scale_color_manual(values = colorselection_channel, 
                     aesthetics = c("colour", "fill"),
                     labels = c("set-3 mRNA", "erm-1 mRNA")) +
  facet_wrap(~ treatment) +
  labs(x = "xpoint", y = "Normalized intensity (mean ± SD)") +
  theme_bw()

a

# Save plot a
#pdf(file = "../03_outputPlots/260527_bmk1_RNAi_by_channel.pdf", width = 4, height = 3)
#print(a)
dev.off()

# ----- Plot 2: split by channel, color by treatment -----
colorselection_treatment <- c("#2189ce", "#000000")
channel.labs <- c(ch1 = "set-3 mRNA", ch2 = "erm-1 mRNA")

b <- ggplot(bmk1_wide_with_stats, 
            aes(x = xpoint, y = mean_signal, 
                group = interaction(channel, treatment))) +
  geom_line(aes(color = treatment)) +
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill = treatment), alpha = 0.2) +
  scale_color_manual(values = colorselection_treatment, 
                     aesthetics = c("colour", "fill"),
                     labels = c("no RNAi", "bmk-1 RNAi")) +
  facet_wrap(~ channel, labeller = labeller(channel = channel.labs)) +
  labs(x = "xpoint", y = "Normalized intensity (mean ± SD)") +
  theme_bw()

b

# Save plot b
#pdf(file = "../03_outputPlots/260527_bmk1_RNAi_by_transcript.pdf", width = 4, height = 3)
#print(b)
dev.off()

```
```{r}
ggplot() +
  geom_line(data = bmk1_norm_total,
            aes(x = xpoint, y = normalized_intensity, group = paste(date, embryoID)),
            alpha = 0.3, color = "grey50") +
  geom_line(data = bmk1_wide_with_stats,
            aes(x = xpoint, y = mean_signal),
            color = "red", linewidth = 1) +
  facet_grid(channel ~ treatment) +
  theme_bw()
```

## Try to create a metric of "membrane-y-ness" for each condition combo

I want a metric that reports the ratio of erm-1 intensity signal at "0" (the peak) versus at -100 or +100. I'll
take the average of -100 and +100.

```{r membraneyness, echo = TRUE, warning = FALSE, message = FALSE}

# extract the "peak" at 1 versus the -100 and +100 values
peaks_and_valleys <- bmk1_norm_total %>%
  filter(aligned_row %in% c(-100,1,100))

# Nest the -100, 1, and +100 values into a single cell
nest_pandv <- peaks_and_valleys %>%
  group_by(date, treatment, embryoID, channel) %>%
  nest()

# A function to calculate the ratio of the value at 1 compared to the mean of -100 and +100
my_calc2 <- function(df) {
  df$normalized_intensity[2] / mean(df$normalized_intensity[1], df$normalized_intensity[3])
}

# Calculate the ratio for each datapoint
foldChange_calc <- nest_pandv %>%
  mutate(fc_enrich = map_dbl(data, my_calc2))

# Change some columns to factors
foldChange_calc$treatment <- as.factor(foldChange_calc$treatment)
foldChange_calc$channel <- as.factor(foldChange_calc$channel)

# calculate the max & min - figure out how to set the y-axis
summary(log(foldChange_calc$fc_enrich, base = 2))

# plot the data:
d <- ggplot(data = foldChange_calc, aes(x = as.factor(channel), y = log(fc_enrich, base = 2), fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 2)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("0uM" = "darkgray", "150uM" = "lightblue"))+
  labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -100 and 100)", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 14)

d

e <- ggplot(data = foldChange_calc, aes(x = as.factor(treatment), y = log(fc_enrich, base = 2), fill = channel))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  scale_y_continuous(limits = c(-0.5, 2)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(y = "log2 FoldChange Enrichment of mRNA \n(mRNA intensity at 0 / mean mRNA intensity at -100 and 100)", x = "mRNA") +
  theme_classic(base_size = 14)

e

getwd()

```

## Save the datasets

```{print_data, echo = TRUE, warning = FALSE, message = FALSE}

# set plotname
today <- format(Sys.Date(), "%y%m%d")
filename <- paste("../03_outputPlots/", today, "_set3_erm1_boxplot_nocodazole1.pdf", sep = "")

pdf(filename, width = 6, height = 6)
d
dev.off()

getwd()


```

## Calculate the statistics

```{r wilcox, echo = TRUE, warning = FALSE, message = FALSE}

foldChange_calc

stats_wilcox <- foldChange_calc %>%
  group_by(channel) %>%
  wilcox_test(fc_enrich ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox




```



## Session info

```{r sessionInfo, echo = TRUE, warning = FALSE, message = FALSE}

sessionInfo()

```