---
title: "260619_KLP-9_L4440_no_alignment"
author: "Sam Zavislan-Pullaro"
date: "2026-06-19"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

Note: this version does NOT align embryos to their individual erm-1 intensity peak.
Peak-alignment assumes every embryo has a well-defined single peak to align to, which
may not hold for klp-9 RNAi embryos with disrupted membrane localization (see discussion
in the original aligned version). Instead, this version uses a fixed re-centering of
xpoint (the scan-window midpoint) so every embryo uses the same x-axis definition,
regardless of treatment or whether it has a detectable peak.

## load libraries

```{r setup, echo = TRUE, warning = FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
library(data.table)
library(rstatix)

```


## Import the data that was outputted from the new macro:

Note: 

channel 1 = set-3

channel 2 = erm-1

```{r macroimport, echo = TRUE, warning = FALSE, message = FALSE}
# import the control data
# control data comes from L4440 empty vector RNAi controls 
control_1 <- read.table(file = "../01_input/2026-6-17_1450_datafile_for_230713_L4440_RNAi_rep1.txt", header = FALSE, sep = "\t")
control_2 <- read.table(file = "../01_input/2026-6-17_153_datafile_for_230828_L4440_RNAi_rep2.txt", header = FALSE, sep = "\t")
control_3 <- read.table(file = "../01_input/2026-6-17_158_datafile_for_240122_LP306_L4440-rep3.txt", header = FALSE, sep = "\t")


# import RNAi treatment data 
test_1 <- read.table(file = "../01_input/2026-5-26_1525_datafile_for_231207_LP306_KLP-9.txt", header = FALSE, sep = "\t")
test_2 <- read.table(file = "../01_input/2026-5-26_1616_datafile_for_231208_LP306_KLP-9_rep2.txt", header = FALSE, sep = "\t")
test_3 <- read.table(file = "../01_input/2026-6-19_1410_datafile_for_231224_LP306_klp-9_RNAi_rep3.txt", header = FALSE, sep = "\t")

# test its dimensions
#dim(control_1)
#dim(control_2)
#dim(test_1)
#dim(test_2)
#dim(test_3)
#dim(test_4)

# Rename the column names
col_times <- paste(rep(1:334), sep = "")
colnames(control_1) <- c("file", "channel", col_times)
colnames(control_2) <- c("file", "channel", col_times)
colnames(control_3) <- c("file", "channel", col_times)

colnames(test_1) <- c("file", "channel", col_times)
colnames(test_2) <- c("file", "channel", col_times)
colnames(test_3) <- c("file", "channel", col_times)

# Check that the dimensions remain unchanged
dim(control_1)
dim(control_2)
dim(control_3)

dim(test_1)
dim(test_2)
dim(test_3)


# control_1[1:9,1:8]
# control_2[1:9,1:8]
# control_3[1:9,1:8]

# test_1[1:9,1:8]
# test_2[1:9,1:8]
# test_3[1:9,1:8]
# test_4[1:9,1:8]

```


## Create annotation columns

```{r annotationcolumns, echo = TRUE, warning = FALSE, message = FALSE}

# Extract out the salient information from the filename and pivot the data longer - "permed" version
# Had to manually change image names to follow convention/consistency

control_1_exp <- control_1[2:dim(control_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_2_exp <- control_2[2:dim(control_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
 
control_3_exp <- control_3[2:dim(control_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_")) 

 
test_1_exp <- test_1[2:dim(test_1)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_2_exp <- test_2[2:dim(test_2)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))

test_3_exp <- test_3[2:dim(test_3)[1],1:335] %>%
  separate_wider_delim(file, delim = "_", names = c("date", "strain", "treatment", "embryoID", NA)) %>%
  pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
  mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))


```

```{r}
# Add in the timepoints

addInTimepoints <- function(tibble) {
  timepoints <- as.vector(unlist(control_1[1,3:335]))
  repnumb = dim(tibble)[1]/333
  tibble::add_column(tibble, timepoints = rep(timepoints,repnumb), .after = "xpoint")
}

control_1_plustime <- addInTimepoints(control_1_exp)
control_2_plustime <- addInTimepoints(control_2_exp)
control_3_plustime <- addInTimepoints(control_3_exp)

test_1_plustime <- addInTimepoints(test_1_exp)
test_2_plustime <- addInTimepoints(test_2_exp)
test_3_plustime <- addInTimepoints(test_3_exp)

#check it
control_1_plustime[330:340,]
control_2_plustime[330:340,]
test_1_plustime[330:340,]
test_2_plustime[330:340,]
test_3_plustime[330:340,]
```

```{r}

# Merge the datasets together 
klp9_RNAi_data_total <- rbind(control_1_plustime, control_2_plustime, control_3_plustime, test_1_plustime, test_2_plustime, test_3_plustime)

# Plot it - all samples
ggplot(data = klp9_RNAi_data_total, aes(x = timepoints, y = intensity, group = c(unique_id))) +
  geom_line(aes(colour = unique_id))+
  facet_wrap(~ channel + treatment)+
  guides(color = "none")+
  theme_bw()

```


## Re-center xpoint to a fixed reference (no peak-alignment)

Rather than aligning each embryo to its own intensity peak (which assumes every embryo
has one well-defined peak to align to), this re-centers `xpoint` using a single fixed
reference point: the midpoint of the scan window. Every embryo, regardless of treatment
or channel, gets the same x-axis definition - so embryos are never excluded or shifted
based on where any individual peak happens to fall.

```{r recenter, echo = TRUE, warning = TRUE, message = TRUE}

# xpoint runs 1:333 for every embryo, so the midpoint of the scan window is:
scan_midpoint <- (1 + 333) / 2  # = 167

# Recentered_row uses the SAME fixed reference for every embryo/channel/treatment -
# no which.max(), no per-embryo alignment, no embryos dropped or shifted differently.
klp9_RNAi_data_total$xpoint <- as.integer(klp9_RNAi_data_total$xpoint)
klp9_RNAi_data_total <- klp9_RNAi_data_total %>%
  mutate(recentered_row = xpoint - scan_midpoint)

# Quick check - every embryo should span the same recentered_row range
klp9_RNAi_data_total %>%
  group_by(unique_id) %>%
  summarize(min_row = min(recentered_row), max_row = max(recentered_row), .groups = "drop") %>%
  summary()

# This replaces total_align_long from the aligned-pipeline version
total_align_long <- klp9_RNAi_data_total %>%
  rename(intensity_raw = intensity) %>%
  mutate(intensity = intensity_raw) %>%
  select(-intensity_raw) %>%
  rename(aligned_row = recentered_row)  # kept as "aligned_row" so downstream code/column names need no further changes

```

```{r}
total_align_long %>%
  group_by(aligned_row) %>%
  summarize(
    n_total = n(),
    n_na = sum(is.na(intensity)),
    pct_na = mean(is.na(intensity)) * 100
  ) %>%
  arrange(aligned_row) %>%
  print(n = Inf)
```


## re-arrange the dataset and calculate the means 

```{r meanplot, echo = TRUE, warning = FALSE, message = FALSE}

# Normalize the data by dividing by the embryo-specific mean
klp9_norm_total <- total_align_long %>%
  separate_wider_delim(unique_id, delim = "_", names = c("date", NA, "treatment", "embryoID", "channel")) %>%
  mutate(treatment = case_when(
    str_to_lower(treatment) == "klp-9" ~ "klp-9",
    str_to_lower(treatment) == "l4440" ~ "L4440",
    TRUE ~ treatment
  )) %>%
  group_by(date, embryoID, channel, treatment) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE))

head(klp9_norm_total)

# Separate out the unique identifier info, then pivot sider
klp9_wide_by_sample <- klp9_norm_total %>%
  pivot_wider(names_from = c(date, embryoID, channel, treatment), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row))


# Second Try - Separate out the unique identifier info, then pivot sider
klp9_wide_by_sample <- klp9_norm_total %>%
  pivot_wider(names_from = c(date, embryoID), 
            values_from = normalized_intensity,
            id_cols = c(strain, aligned_row, treatment, channel))



colnames(klp9_wide_by_sample)
# Play around with mean, medium, and sum:
klp9_wide_with_stats <- klp9_wide_by_sample %>%
  rowwise() %>%
  mutate(
    sum_signal    = sum(c_across(`230713_03`:`231224_08`), na.rm = TRUE),
    mean_signal   = mean(c_across(`230713_03`:`231224_08`), na.rm = TRUE),
    median_signal = median(c_across(`230713_03`:`231224_08`), na.rm = TRUE),
    sd_signal     = sd(c_across(`230713_03`:`231224_08`), na.rm = TRUE)
  ) %>%
  ungroup()

# colnames(klp9_wide_with_stats)

klp9_wide_with_range <- klp9_wide_with_stats %>%
  rowwise() %>%
  mutate(ymeanmax = sum(mean_signal, sd_signal) ) %>%
  mutate(ymeanmin = sum(mean_signal, -sd_signal)) 

colorselection = c("#000000", "#2189ce")


# Plot split by Nocodazole concentration
a <- ggplot(data = klp9_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=channel))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("set-3 mRNA", "erm-1 mRNA"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=channel), alpha = 0.2, ) +
  facet_wrap(~ treatment)+
  theme_bw()

a


#pdf(file = "../03_outputPlots/260315_erm_set3_nocodazole.pdf", width = 4, height = 3)

a

dev.off()


# Plot in a different way - set-3 and erm-1 mRNA split into facets
colorselection = c("#2189ce", "#000000")
channel.labs <- c("set-3 mRNA", "erm-1 mRNA")
names(channel.labs) <- c("ch1", "ch2")

# Plot split by transcript
b <- ggplot(data = klp9_wide_with_range, aes(x = aligned_row, y = mean_signal, group = interaction(channel, treatment)))+
  geom_line(aes(color=treatment))+
  scale_color_manual(values = colorselection, aesthetics = c("colour", "fill"), labels = c("no RNAi", "klp-9 RNAi"))+
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax, fill=treatment), alpha = 0.2, ) +
  facet_wrap(~ channel, labeller = labeller(channel = channel.labs))+
  theme_bw()

b


# pdf(file = "../03_outputPlots/260315_erm_set3_nocodazole_bytranscript.pdf", width = 4, height = 3)
# 
# b

dev.off()

###### THIS IS WRONG!!!!

```


## Try to create a metric of "membrane-y-ness" for each condition combo

I want a metric that reports the ratio of erm-1 intensity signal at its peak versus at
the flanks. Importantly, since this version does NOT align embryos to their own peak,
`aligned_row == 1` is just the fixed scan-window midpoint - NOT necessarily where any
given embryo's actual intensity peak is. So instead, for each embryo we find its own true
max intensity (wherever it falls along the trace) and compare it to the mean intensity at
the far left and far right ends of that embryo's trace (its "flanks"). This keeps the
same biological question (peak vs. flanks) without requiring any embryo to be
re-centered or excluded based on alignment.

```{r membraneyness, echo = TRUE, warning = FALSE, message = FALSE}

# For each embryo/channel, find:
#   - peak_intensity = the embryo's own true max normalized_intensity (wherever it falls)
#   - flank_intensity = mean of normalized_intensity at the far left & far right ends of
#     its trace (using the min and max available aligned_row per embryo, so this works
#     even though every embryo's trace already spans the same fixed aligned_row range)
foldChange_calc <- klp9_norm_total %>%
  group_by(date, treatment, embryoID, channel) %>%
  summarize(
    peak_intensity = max(normalized_intensity, na.rm = TRUE),
    flank_intensity = mean(
      normalized_intensity[aligned_row %in% range(aligned_row, na.rm = TRUE)],
      na.rm = TRUE
    ),
    fc_enrich = peak_intensity / flank_intensity,
    .groups = "drop"
  )

# Change some columns to factors
foldChange_calc$treatment <- as.factor(foldChange_calc$treatment)
foldChange_calc$channel <- as.factor(foldChange_calc$channel)

# Confirm no embryos were dropped (n per treatment/channel should match raw embryo counts)
foldChange_calc %>% count(treatment, channel)

# calculate the max & min - figure out how to set the y-axis
summary(log(foldChange_calc$fc_enrich, base = 2))

# plot the data:
d <- ggplot(data = foldChange_calc, aes(x = as.factor(channel), y = log(fc_enrich, base = 2), fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(y = "log2 FoldChange Enrichment of mRNA \n(peak mRNA intensity / mean mRNA intensity at trace flanks)", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 14)

d

e <- ggplot(data = foldChange_calc, aes(x = as.factor(treatment), y = log(fc_enrich, base = 2), fill = channel))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position=position_jitterdodge())+
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(y = "log2 FoldChange Enrichment of mRNA \n(peak mRNA intensity / mean mRNA intensity at trace flanks)", x = "mRNA") +
  theme_classic(base_size = 14)

e

getwd()

```
```{r}
library(dplyr)

foldChange_calc %>%
  group_by(treatment, channel) %>%
  summarise(
    min_val    = min(log(fc_enrich, base = 2), na.rm = TRUE),
    median_val = median(log(fc_enrich, base = 2), na.rm = TRUE),
    max_val    = max(log(fc_enrich, base = 2), na.rm = TRUE)
  )
```
```{r}
foldChange_calc %>%
  mutate(log2_fc = log(fc_enrich, base = 2)) %>%
  group_by(treatment, channel) %>%
  slice(c(
    which.min(log2_fc),
    which(log2_fc == median(log2_fc)), 
    which.max(log2_fc)
  ))
```

## Alternative "membrane-y-ness" metric: coefficient of variation

The fc_enrich metric above still relies on finding each embryo's own peak intensity,
which assumes there IS a well-defined peak to find. For klp-9 RNAi embryos where
membrane signal may be disrupted/diffuse, this may not hold well.

As a fully complementary check that doesn't rely on identifying any peak at all, this
calculates the coefficient of variation (CV = sd / mean) of normalized_intensity across
the whole trace for every embryo. A sharp, well-localized membrane signal should give a
high CV (most of the trace near baseline, with one strong spike); a flat/diffuse signal
(disrupted membrane) should give a low CV (intensity is similar everywhere along the
trace). This uses every embryo with intensity data and makes no assumptions about where,
or whether, a peak exists.

```{r membraneyness_cv, echo = TRUE, warning = FALSE, message = FALSE}

# Calculate per-embryo CV directly from klp9_norm_total (no peak-alignment dependency)
cv_metric <- klp9_norm_total %>%
  group_by(date, treatment, embryoID, channel) %>%
  summarize(
    n_points = sum(!is.na(normalized_intensity)),
    mean_intensity = mean(normalized_intensity, na.rm = TRUE),
    sd_intensity = sd(normalized_intensity, na.rm = TRUE),
    cv = sd_intensity / mean_intensity,
    .groups = "drop"
  )

# Confirm no embryos were dropped (n per treatment/channel should match your earlier raw counts)
cv_metric %>% count(treatment, channel)

# Change some columns to factors (matches foldChange_calc conventions)
cv_metric$treatment <- as.factor(cv_metric$treatment)
cv_metric$channel <- as.factor(cv_metric$channel)

# quick look at the distribution
summary(cv_metric$cv)

# plot the data: CV by channel, split by treatment
f <- ggplot(data = cv_metric, aes(x = as.factor(channel), y = cv, fill = treatment))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position = position_jitterdodge())+
  labs(y = "Coefficient of Variation (sd / mean) of mRNA intensity\nacross full trace", x = "mRNA") +
  scale_x_discrete(labels = c("ch1" = "set-3", "ch2" = "erm-1"))+
  theme_classic(base_size = 14)

f

# plot the data: CV by treatment, split by channel
g <- ggplot(data = cv_metric, aes(x = as.factor(treatment), y = cv, fill = channel))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(position = position_jitterdodge())+
  labs(y = "Coefficient of Variation (sd / mean) of mRNA intensity\nacross full trace", x = "treatment") +
  theme_classic(base_size = 14)

g

# Stats: same approach as the fc_enrich wilcox test, for direct comparison
stats_wilcox_cv <- cv_metric %>%
  group_by(channel) %>%
  wilcox_test(cv ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox_cv

```


## Save the datasets

```{r print_data, echo = TRUE, warning = FALSE, message = FALSE}

# set plotname
today <- format(Sys.Date(), "%y%m%d")
filename <- paste("../03_outputPlots/", today, "klp-9_L4440_no_alignment.pdf", sep = "")

pdf(filename, width = 6, height = 6)
d
dev.off()

getwd()


```

## Calculate the statistics

```{r wilcox, echo = TRUE, warning = FALSE, message = FALSE}

foldChange_calc

stats_wilcox <- foldChange_calc %>%
  group_by(channel) %>%
  wilcox_test(fc_enrich ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

stats_wilcox




```



## Session info

```{r sessionInfo, echo = TRUE, warning = FALSE, message = FALSE}

sessionInfo()

```