---
title: "bmk-1 RNAi — 4-cell Stage Merged Analysis (ABa-ABp & ABa-EMS)"
author: "Sam Zavislan-Pullaro"
date: "2026-07-14"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: flatly
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 6)
```

## Load libraries

```{r setup}
library(tidyverse)
library(data.table)
library(rstatix)
library(ggrepel)
library(gridExtra)
```

---

## Import data

Note: channel 1 = set-3 mRNA | channel 2 = erm-1 mRNA

Each cell-pair experiment has its own set of L4440 controls (measured
separately) and is kept distinct throughout until the combined boxplot.
Membraneyness is calculated using positions ±50 (matching the individual
4-cell scripts), not ±100 used in the 2-cell analysis.

```{r import}

col_times <- paste(rep(1:333), sep = "")

set_cols <- function(df) {
  colnames(df) <- c("file", "channel", col_times)
  df
}

# ── ABa-ABp controls (4 reps) ────────────────────────────────────────────────
abp_ctrl_1 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-11_1324_datafile_for_231107_LP306_L4440.txt",       header = FALSE, sep = "\t"))
abp_ctrl_2 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-11_1252_datafile_for_230713_L4440_RNAi_rep1.txt",    header = FALSE, sep = "\t"))
abp_ctrl_3 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-11_133_datafile_for_230828_L4440_RNAi_rep2.txt",     header = FALSE, sep = "\t"))
abp_ctrl_4 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-11_1337_datafile_for_240122_LP306_L4440-rep3.txt",   header = FALSE, sep = "\t"))

# ── ABa-ABp bmk-1 RNAi (4 reps) ─────────────────────────────────────────────
abp_test_1 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-14_126_datafile_for_220719_LP306_bmk-1_RNAi.txt",    header = FALSE, sep = "\t"))
abp_test_2 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-14_1216_datafile_for_230408_LP306_BMK-1_rep1.txt",   header = FALSE, sep = "\t"))
abp_test_3 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-14_1222_datafile_for_231107_LP306_BMK-1_rep2.txt",   header = FALSE, sep = "\t"))
abp_test_4 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-ABp/01_input/2026-7-14_1225_datafile_for_231113_LP306_BMK-1_rep3.txt",   header = FALSE, sep = "\t"))

# ── ABa-EMS controls (4 reps) ────────────────────────────────────────────────
ems_ctrl_1 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-11_1329_datafile_for_231107_LP306_L4440.txt",        header = FALSE, sep = "\t"))
ems_ctrl_2 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-11_1257_datafile_for_230713_L4440_RNAi_rep1.txt",    header = FALSE, sep = "\t"))
ems_ctrl_3 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-11_1311_datafile_for_230828_L4440_RNAi_rep2.txt",    header = FALSE, sep = "\t"))
ems_ctrl_4 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-11_1346_datafile_for_240122_LP306_L4440-rep3.txt",   header = FALSE, sep = "\t"))

# ── ABa-EMS bmk-1 RNAi (4 reps) ─────────────────────────────────────────────
ems_test_1 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-14_1233_datafile_for_220719_LP306_bmk-1_RNAi.txt",   header = FALSE, sep = "\t"))
ems_test_2 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-14_1238_datafile_for_230408_LP306_BMK-1_rep1.txt",   header = FALSE, sep = "\t"))
ems_test_3 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-14_1241_datafile_for_231107_LP306_BMK-1_rep2.txt",   header = FALSE, sep = "\t"))
ems_test_4 <- set_cols(read.table("../bmk-1_RNAi_4-cell_ABa-EMS/01_input/2026-7-14_1244_datafile_for_231113_LP306_BMK-1_rep3.txt",   header = FALSE, sep = "\t"))

```

---

## Annotate, merge, and apply fixed coordinate alignment

```{r annotate_merge}

annotate_df <- function(df) {
  df[2:nrow(df), 1:335] %>%
    separate_wider_delim(file, delim = "_",
                         names = c("date", "strain", "treatment", "embryoID", NA)) %>%
    pivot_longer(cols = `1`:`333`, names_to = "xpoint", values_to = "intensity") %>%
    mutate(unique_id = paste(date, strain, treatment, embryoID, channel, sep = "_"))
}

addInTimepoints <- function(tibble, ref_table) {
  timepoints <- as.vector(unlist(ref_table[1, 3:335]))
  repnumb    <- nrow(tibble) / 333
  tibble::add_column(tibble, timepoints = rep(timepoints, repnumb), .after = "xpoint")
}

proc <- function(df, ref_df, pair_label) {
  addInTimepoints(annotate_df(df), ref_df) %>%
    mutate(cell_pair = pair_label)
}

all_4cell <- rbind(
  proc(abp_ctrl_1, abp_ctrl_1, "ABa-ABp"), proc(abp_ctrl_2, abp_ctrl_1, "ABa-ABp"),
  proc(abp_ctrl_3, abp_ctrl_1, "ABa-ABp"), proc(abp_ctrl_4, abp_ctrl_1, "ABa-ABp"),
  proc(abp_test_1, abp_ctrl_1, "ABa-ABp"), proc(abp_test_2, abp_ctrl_1, "ABa-ABp"),
  proc(abp_test_3, abp_ctrl_1, "ABa-ABp"), proc(abp_test_4, abp_ctrl_1, "ABa-ABp"),
  proc(ems_ctrl_1, ems_ctrl_1, "ABa-EMS"), proc(ems_ctrl_2, ems_ctrl_1, "ABa-EMS"),
  proc(ems_ctrl_3, ems_ctrl_1, "ABa-EMS"), proc(ems_ctrl_4, ems_ctrl_1, "ABa-EMS"),
  proc(ems_test_1, ems_ctrl_1, "ABa-EMS"), proc(ems_test_2, ems_ctrl_1, "ABa-EMS"),
  proc(ems_test_3, ems_ctrl_1, "ABa-EMS"), proc(ems_test_4, ems_ctrl_1, "ABa-EMS")
)

dt_4cell <- as.data.table(all_4cell)
dt_4cell$xpoint <- as.integer(dt_4cell$xpoint)
dt_4cell[, aligned_row := xpoint - 167]

align_4cell <- dt_4cell %>%
  select(cell_pair, strain, aligned_row, unique_id, intensity)

cat("Total rows:", nrow(align_4cell), "\n")
cat("Unique embryo IDs:", n_distinct(align_4cell$unique_id), "\n")

```

---

## Normalize

```{r normalize}

norm_4cell <- align_4cell %>%
  separate_wider_delim(unique_id, delim = "_",
                       names = c("date", NA, "treatment", "embryoID", "channel")) %>%
  group_by(date, embryoID, channel, treatment, cell_pair) %>%
  mutate(normalized_intensity = intensity / mean(intensity, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    treatment      = factor(treatment, levels = c("L4440", "bmk-1")),
    treatment_type = ifelse(treatment == "L4440", "L4440", "RNAi")
  )

table(norm_4cell$channel, norm_4cell$treatment, norm_4cell$cell_pair)

```

---

## Color palettes

```{r palettes}

type_colors    <- c("L4440" = "darkgray", "RNAi" = "lightblue")
channel_labels <- c("ch1" = "set-3 mRNA", "ch2" = "erm-1 mRNA")

```

---

## Section 1: Individual normalized line scans

```{r linescans_individual, fig.height = 8, fig.width = 12}

ggplot(norm_4cell,
       aes(x = aligned_row, y = normalized_intensity,
           group = interaction(date, embryoID),
           color = treatment)) +
  geom_line(alpha = 0.4, linewidth = 0.3) +
  scale_color_manual(values = c("L4440" = "gray50", "bmk-1" = "lightblue4")) +
  facet_grid(channel ~ cell_pair + treatment,
             labeller = labeller(channel = channel_labels)) +
  labs(
    title = "Individual normalized line scans — ABa-ABp and ABa-EMS",
    x     = "Position (aligned_row)",
    y     = "Normalized intensity"
  ) +
  guides(color = "none") +
  theme_bw(base_size = 11) +
  theme(strip.text = element_text(face = "bold"))

```

---

## Section 2: Mean ± SD line scans

```{r linescans_mean, fig.height = 6, fig.width = 12}

mean_signal <- norm_4cell %>%
  group_by(aligned_row, treatment, channel, cell_pair) %>%
  summarize(
    mean_signal = mean(normalized_intensity, na.rm = TRUE),
    sd_signal   = sd(normalized_intensity,   na.rm = TRUE),
    .groups     = "drop"
  ) %>%
  mutate(
    ymeanmax = mean_signal + sd_signal,
    ymeanmin = mean_signal - sd_signal,
    group_id = interaction(treatment, cell_pair)
  )

ggplot(mean_signal,
       aes(x = aligned_row, y = mean_signal,
           color = treatment, linetype = cell_pair,
           group = group_id)) +
  geom_ribbon(aes(ymin = ymeanmin, ymax = ymeanmax,
                  fill = treatment), alpha = 0.15, color = NA) +
  geom_line(linewidth = 0.8) +
  scale_color_manual(values = c("L4440" = "gray50", "bmk-1" = "lightblue4")) +
  scale_fill_manual(values  = c("L4440" = "gray50", "bmk-1" = "lightblue4")) +
  facet_wrap(~ channel, labeller = labeller(channel = channel_labels)) +
  labs(
    title    = "Mean ± SD normalized line scans — ABa-ABp and ABa-EMS",
    x        = "Position (aligned_row)",
    y        = "Mean normalized intensity",
    color    = "Treatment",
    linetype = "Cell pair"
  ) +
  theme_bw(base_size = 12) +
  theme(strip.text = element_text(face = "bold"),
        legend.position = "right")

```

---

## Section 3: Membraneyness — log2 fold change

Ratio of normalized intensity at position 1 versus the mean of positions
-50 and +50, matching the individual 4-cell scripts.

```{r membraneyness}

my_calc2 <- function(df) {
  df$normalized_intensity[2] /
    mean(c(df$normalized_intensity[1], df$normalized_intensity[3]))
}

fc_4cell <- norm_4cell %>%
  filter(aligned_row %in% c(-50, 1, 50)) %>%
  group_by(date, treatment, embryoID, channel, cell_pair) %>%
  nest() %>%
  mutate(fc_enrich = map_dbl(data, my_calc2)) %>%
  ungroup() %>%
  mutate(
    log2_fc        = log(fc_enrich, base = 2),
    treatment_type = ifelse(treatment == "L4440", "L4440", "RNAi"),
    treatment      = factor(treatment, levels = c("L4440", "bmk-1"))
  )

summary(fc_4cell$log2_fc)

```

### 3a. Merged boxplot — separate controls per cell pair

x-axis = cell pair, fill = treatment. Each cell pair's L4440 control stays
paired with its own bmk-1 RNAi group.

```{r boxplot_merged, fig.height = 6, fig.width = 8}

p_merged <- ggplot(fc_4cell,
                   aes(x = cell_pair, y = log2_fc, fill = treatment_type)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  geom_jitter(aes(color = treatment_type),
              position = position_jitterdodge(jitter.width = 0.2),
              size = 1.5, alpha = 0.7) +
  scale_fill_manual(
    values = type_colors,
    labels = c("L4440" = "L4440 control", "RNAi" = "bmk-1 RNAi")
  ) +
  scale_color_manual(
    values = c("L4440" = "gray30", "RNAi" = "#1a6fa0"),
    guide  = "none"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  facet_wrap(~ channel, labeller = labeller(channel = channel_labels)) +
  labs(
    title = "4-cell bmk-1 RNAi — membraneyness (separate controls)",
    x     = "Cell pair",
    y     = "log2 (intensity at 0 / mean intensity at ±50)",
    fill  = NULL
  ) +
  theme_classic(base_size = 12) +
  theme(
    strip.text      = element_text(face = "bold"),
    legend.position = "top"
  )

p_merged

```

### 3b. Combined boxplot — controls and treatments pooled

ABa-ABp and ABa-EMS L4440 controls are combined into one L4440 group;
both bmk-1 RNAi sets are combined into one bmk-1 group.

```{r boxplot_combined, fig.height = 6, fig.width = 6}

p_combined <- ggplot(fc_4cell,
                     aes(x = treatment, y = log2_fc, fill = treatment_type)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  geom_jitter(aes(color = treatment_type),
              position = position_jitterdodge(jitter.width = 0.2),
              size = 1.5, alpha = 0.7) +
  scale_fill_manual(
    values = type_colors,
    labels = c("L4440" = "L4440 control", "RNAi" = "bmk-1 RNAi")
  ) +
  scale_color_manual(
    values = c("L4440" = "gray30", "RNAi" = "#1a6fa0"),
    guide  = "none"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  facet_wrap(~ channel, labeller = labeller(channel = channel_labels)) +
  labs(
    title = "4-cell bmk-1 RNAi — membraneyness (pooled)",
    x     = "Treatment",
    y     = "log2 (intensity at 0 / mean intensity at ±50)",
    fill  = NULL
  ) +
  theme_classic(base_size = 12) +
  theme(
    axis.text.x     = element_text(face = "italic"),
    strip.text      = element_text(face = "bold"),
    legend.position = "top"
  )

p_combined

```

---

## Summary statistics

```{r summary_stats}

fc_4cell %>%
  group_by(treatment, channel, cell_pair) %>%
  summarise(
    n             = n(),
    median_log2fc = round(median(log2_fc, na.rm = TRUE), 3),
    mean_log2fc   = round(mean(log2_fc,   na.rm = TRUE), 3),
    sd_log2fc     = round(sd(log2_fc,     na.rm = TRUE), 3),
    .groups = "drop"
  ) %>%
  arrange(channel, cell_pair, treatment) %>%
  print(n = Inf)

```

---

## Statistics

### Per cell pair — Wilcoxon L4440 vs bmk-1

```{r stats_per_pair}

fc_4cell %>%
  group_by(channel, cell_pair) %>%
  wilcox_test(log2_fc ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

```

### Pooled — Wilcoxon L4440 vs bmk-1

```{r stats_pooled}

fc_4cell %>%
  group_by(channel) %>%
  wilcox_test(log2_fc ~ treatment) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()

```

---

## Save plots

```{r save_plots}

today    <- format(Sys.Date(), "%y%m%d")
pdf_path <- paste0("./", today, "_4cell_bmk1_merged_plots.pdf")

pdf(pdf_path, width = 10, height = 6)
  print(p_merged)
  print(p_combined)
dev.off()

cat("Plots saved to:", pdf_path, "\n")

```

---

## Session info

```{r sessionInfo}
sessionInfo()
```
